---
title: "SMR-SAM Run Report"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

``` {r, echo=FALSE}
source("source_SMR.R") # right now this only works when run as a code --> i need to functionalize source_SMR and turn this into a parameterized report
# where location and mapset are specified at the top of the document --> right now they are readlin() inputs in the source_SMR script and that gets skipped during 
# the knit
```

```{r, echo=FALSE, include=FALSE}
source("functional_PP.R", local = knitr::knit_global())
```

```{r, include=FALSE}

user <- Sys.info()["user"]
validation_data_path <- paste0("/Users/", user,"/Dropbox/SMR_R/raw_data/discharge_historical/USGSdischarge.csv")
modeled_data_path <- paste0("/Users/", user,"/Dropbox/SMR_R/raw_data/smr_output/MFC_mass_balance_79.csv")

column_headers <- c('wshed_id', 'date', 'year', 'runoff_cm', 'precip_cm', 'rain_cm', 'actualET_flow_cm', 'canopy_evap_cm', 'snowmelt_cm', 'storage_amt_cm', 'throughfall_cm', 'canopy_storage_amt_cm', 'perc_cm', 'Q', 'swe_cm', 'condens_cm', 'snow_cm', 'baseflow', 'srad', 'latent', 'sensible', 'lw', 'q_rain_ground', 'q_total', 'ice_content', 'liquid_water', 'refreeze', 'vap_d_air', 'vap_d_snow', 'u_surface', 'empty') # this should be based on the line in the perl script writing them out so we don't have to worry about changing it

start_date <- "1965-10-01" # this can be dynamic based on weather inputs
end_date <- "1970-10-01" # this an be dynamics based on weather inputs
```

## Run Identification:

      Run Date: `r Sys.Date()`
      Modeled Period: `r start_date` to `r end_date`

```{r version_track, echo=FALSE, include=FALSE}
#modeled_path <- "./raw_data/smr_output" # this needs to be a generic name eventually
version_tracker(modeled_path = modeled_data_path)
```

```{r, echo=FALSE, include=FALSE}
VaM_data <- preprocessing(
  validation_data_path,
  modeled_data_path,
  start_date,
  end_date,
  column_headers
)
```

```{r, echo=FALSE}

NSE_Q <- nse_Q(VaM_data)
KGE_Q <- kge_Q(VaM_data)

```

## Model Performance by Metric

      NSE: `r NSE_Q`
      KGE: `r KGE_Q`

## Report Outline:

|   1: Main Visualizations:
|       1.1 Modeled vs. Validation Stream Discharge
|       1.2 Annual Mass Balance
|       1.3 Annual Accumulated Flux
|       1.4 Snow Melt and Accumulation Model Components
|       1.5 Radiation Fluxes

|   2: Map Outputs:
|       2.1 Average Soil Moisture (A Horizon) in February
|       2.2 Average Soil Moisture (B Horizon) in February
|       2.3 Average Runoff in February

|   3: Additional Graphs:
|       3.1 Snow Water Equivalent and its Components
|       3.2 Vapor Density of Air and Snow
|       3.3 Individual Flux Time Series

\newpage

```{r Q_comparison, echo=FALSE, include=FALSE}
Q_comp <- Q_comparison(VaM_data, log_transform = T)
```

```{r Q_comp, echo=FALSE}
Q_comp
```

```{r annual_fluxes, echo=FALSE}
flux_vector <- c('runoff_cm', 'precip_cm', 'rain_cm', 
                 'actualET_flow_cm', 'canopy_evap_cm', 
                 'snowmelt_cm', 'storage_amt_cm', 
                 'throughfall_cm', 'canopy_storage_amt_cm', 
                 'perc_cm', 'swe_cm', 'condens_cm', 
                 'snow_cm', 'baseflow')
annual_fluxes(VaM_data, flux_vector, log_transform = F)
```

```{r radiation_ts, echo=FALSE}
radiation_ts(VaM_data, log_transform = F)
```

```{r SAM_check, echo=FALSE}
SAM_check(VaM_data, log_transform = F)
```

```{r swe_debug, echo=FALSE}
swe_debug(VaM_data, log_transform = F)
```

```{r q.latent_debug, echo=FALSE}
q.latent_debug(VaM_data, log_transform = F)
```

```{r get_map_outputs, echo=FALSE, include=FALSE}
get_map_outputs(
  "/Users/duncanjurayj/Documents/SMR_R/raw_data/smr_output/map_outputs/feb_outputs"
)
```

```{r storage_amt_feb, echo=FALSE}
storage_amt_feb(`avg_A_amt_feb_1969_2023-04-12`, 'A')
```
